### 2022-10-19 manuscript.Rmd
Remove comment

\textcolor{red}{here we now show the shortened original syntax. Is this understandable, or replace with simpler, longer function? (see original ms)}

Here, we define the generate function for the tripartite model. The factor loadings specified in step 2 (Design) are called from the condition argument such that they are varied across different iterations of the simulation, and are defined as a for syntax readability. For standardization purposes (that is, the total variance of each manifest variable summing up to 1), the loadings of indicators Task5 and Task6 are set to $\frac {a}{\sqrt{(2+2 \cdot cov1)}}$ to account for cross-loadings on multiple factors and are defined as b to ease syntax readability (cov1 = covariance between the latent factors pattern separation and pattern completion). The population model is defined by a model string, which specifies three latent factors (ps, pc, gen), measured by the 13 manifest indicators (task1 – task13). The residual variances of the manifest variables are set to $1-a^2$ for standardization purposes. The covariance between the latent factors is set to the respective value from the condition argument. The data are simulated from the model syntax via the simulateData() function from the lavaan package and stored as dat. For the sake of clarity, all loadings and co-variances are spelled out separately (but see supplementary R code on GitHub for rewriting the same model in a more concise syntax).

>>>>

Here, we define the generate function for the tripartite model. The factor loadings specified in step 2 (Design) are called from the condition argument such that they are varied across different iterations of the simulation, and are defined as a for syntax readability. For standardization purposes (that is, the total variance of each manifest variable summing up to 1), the loadings of indicators Task5 and Task6 are set to $\frac {a}{\sqrt{(2+2 \cdot cov1)}}$ to account for cross-loadings on multiple factors and are defined as b to ease syntax readability (cov1 = covariance between the latent factors pattern separation and pattern completion). The population model is defined by a model string, which specifies three latent factors (ps, pc, gen), measured by the 13 manifest indicators (task1 – task13). The residual variances of the manifest variables are set to $1-a^2$ for standardization purposes. The covariance between the latent factors is set to the respective value from the condition argument. The data are simulated from the model syntax via the simulateData() function from the lavaan package and stored as dat.
